---
title: "R Notebook"
output: html_notebook
---
Getting insert data formatted for TASSEL- works with VCF not HAPMAP.

```{r}
setwd("~/Box Sync/Landrace/workdir")
library("reshape2", lib.loc="/Library/Frameworks/R.framework/Versions/3.3/Resources/library")
library(plyr)
library(stringr)
insert <- read.csv("Insertion_data.csv")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.
```{r}
insert1 <- insert[,c(3,11:15,17:21)]
insertmelt <- melt(insert1, id=c("COLLECTION"))
insertmelt <- rename(insertmelt, c("value"="genotype"))
insertmelt <- rename(insertmelt, c("variable"="locus"))
insertmelt$plant_id <- str_sub(insertmelt$locus, -1, -1)
insertmelt$sample_id <- paste(insertmelt$COLLECTION, "_", insertmelt$plant_id)
insertmelt <- insertmelt[,c(1,2,3,5)]
```

subset by locus
```{r}
CACTA <- insertmelt[grep("CACTA", insertmelt$locus), ]
CACTA <- rename(CACTA, c("genotype"="CACTA"))
MITE <- insertmelt[grep("MITE", insertmelt$locus), ]
MITE <- rename(MITE, c("genotype"="MITE"))
hap <- merge(CACTA, MITE, by="sample_id")
hap <- hap[,c(1,4,7)]
hap <- na.omit(hap)
```


```{r}
hap$CACTA <- gsub("-1", "./.", hap$CACTA)
hap$MITE <- gsub("-1", "./.", hap$MITE)
hap$CACTA <- gsub("1", "1/0", hap$CACTA)
hap$CACTA <- gsub("2", "1/1", hap$CACTA)
hap$CACTA <- gsub("0", "0/0", hap$CACTA)
hap$MITE <- gsub("1", "1/0", hap$MITE)
hap$MITE <- gsub("2", "1/1", hap$MITE)
hap$MITE <- gsub("0", "0/0", hap$MITE)


```


```{r}
header <- c('alleles', 'chrom', 'pos', 'strand', 'assembly#', 'center', 'protLSID', 'assayLSID', 'panel', 'QCcode')
header <- as.data.frame(header)
header$CACTA <- ""
header$MITE <- ""
header <- rename(header, c("header"="sample_id"))
hapm <- rbind(header, hap)
hapm <- rename(hapm, c("sample_id"="rs"))
```

transpose
```{r}
hapmap <- t(hapm)
hapmap <- as.data.frame(hapmap)
colnames(hapmap) = hapmap[1, ]
#hapmap = hapmap[-1, ]
```



```{r}
#write.table(hapmap, file="hapmap_letters.txt", sep = "\t")
```




for vcf- THIS WORKED FOR INPUT INTO TASSEL! 

```{r}
headervcf <- c('CHROM', 'POS', 'ID', 'REF', 'ALT', 'QUAL', 'FILTER', 'INFO', 'FORMAT')
headervcf <- as.data.frame(headervcf)
headervcf$CACTA <- ""
headervcf$MITE <- ""
headervcf <- rename(headervcf, c("headervcf"="sample_id"))
vcf <- rbind(headervcf, hap)
vcf <- rename(vcf, c("sample_id"="ID"))
```

transpose
```{r}
vcffile <- t(vcf)
vcffile <- as.data.frame(vcffile)
colnames(vcffile) = vcffile[1, ]
#hapmap = hapmap[-1, ]
```



```{r}
write.table(vcffile, file="vcffile_letters.txt", sep = "\t")
```
```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
